Estimating Gaze Duration Error from Eye Tracking Data

### 2022-07-03 paper/paper.tex
Refining experiments and paper
Improving experimental results, plotting and paper
Finalising paper draft

For the sake of our simulations we use a fixed sized simulated device with viewport pixel 
dimensions of 350 by 627. Our area of interest (AOI) is a fixed position medium rectangle ad unit (MREC)
that is located toward the top of the screen. We iterate over a range of potential mean error
values (determined to be the mean Euclidean distance between the measured fixation and actual fixation).
For each of these mean error values we generate a synthetic eye tracking calibration file.

@@

The result shown in Figure \ref{fig:measured_vs_expected} is indicative of what we see under
multiple variations of the simulation configuration. At lower meaurement values there is a 
tendency for the measurement to be an over estimation, and at higher values an under-estimation.

@@

\begin{figure}[h!]
\includegraphics[scale=0.5]{../results/Fixation_vs_duration_error.png}
\caption{Fixation error versus gaze duration error.}
\label{fig:fixation_vs_duration}
\end{figure}

As shown in Figure \ref{fig:fixation_vs_duration} we see that the error in gaze duration
grows with error in fixation points, as would be expected. However, when we use the exponential
weighting to calculate the expected error in duration, the gaze duration error grows much slower
than in the uniform case. This suggests that the observed tendency toward smaller measurements
in area of interest studies means lower expected error.

@@

\begin{figure}[h!]
\includegraphics[scale=0.5]{../results/Error_surface.png}
\caption{Mean gaze duration error over measured error and fixation MAE.}
\label{fig:error_surface}
\end{figure}

There is a region in Figure \ref{fig:error_surface} that is unpopulated due to the fact that
the estimated distributions contained no density in these regions. This was observed for 
eye tracking models with high fixation error and when the measured duration was high. Meaning
that our model estimates that when fixation error is this high, measurements of these values
become extremely unlikley to be observed.

>>>>

For the sake of our simulations we use a fixed sized simulated device with viewport pixel 
dimensions of 350 by 627. Our area of interest (AOI) is a fixed position medium rectangle ad unit (MREC)
that is located toward the top of the screen. We iterate over a range of potential mean error
values (determined to be the mean Euclidean distance between the measured fixation and actual fixation).
For each of these mean error values we generate a synthetic eye tracking calibration file. We produce
two versions of this calibration data, one in which the error is distributed around the true target,
and a second biased version in which the error tends toward the upper left of the true position. We 
include the biased calibration data as it is consistent with our observations of real eye tracking data
and we explore the extent to which this bias affects gaze duration measurements.

@@

The result shown in Figure \ref{fig:measured_vs_expected} is indicative of what we see under
multiple variations of the simulation configuration. At lower meaurement values there is a 
tendency for the measurement to be an accurate estimation, while at higher values it tends
toward an under-estimation of the true gaze duration. Surprisingly the results using the
biased calibration data seem to mitigate this effect somewhat, but the overall pattern 
remains consistent.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{../results/Fixation_vs_duration_error.png}
\caption{Fixation error versus gaze duration error.}
\label{fig:fixation_vs_duration}
\end{figure}

As shown in Figure \ref{fig:fixation_vs_duration} we see that the error in gaze duration
grows with error in fixation points, as would be expected. However, when we use the exponential
weighting to calculate the expected error in duration the gaze duration error grows much slower
than in the uniform case. This suggests that the observed tendency toward smaller measurements
in area of interest studies means lower expected error overall. This pattern is true for the 
centrally distributed error (A) as well as the biased calibration error (B).

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{../results/Error_surface.png}
\caption{Mean gaze duration error over measured error and fixation MAE.}
\label{fig:error_surface}
\end{figure}

The left hand plot shows the complete error surface in which you will observe large spikes in
error in the corner correspinding to high MAE for the fixation models and high measurements of
gaze duration. This effect is caused by a complete absence of probability density in these
regions, meaning that the error is maximal because the expected value is zero. This effect 
was consistenlt observed for 
eye tracking models with high fixation error and when the measured duration was high. Meaning
that our model estimates that when fixation error is this high, measurements of these values
become extremely unlikley to be observed.

We added the right hand plot in Figure \ref{fig:error_surface} to illustrate the error surface
in the absence of these deceptive outliers. We see that in general the expected error in a gaze
duration is maximal around the mid point of the measurement range. The effect is lessened by 
lower MAE in the fixation models, but remains consistent for all levels of fixation error.
